### 2023-10-10 letters/cover letter-fdarecurrent-rd2.tex
Update cover letter-fdarecurrent-rd2.tex

>>>>

The source files for the manuscript and supplementary materials are contained in two zip/tar files as requested.  Below is a list of the files names with a brief summary as requested:\\

{\bf Manuscript zip file:} \emph{fda-recurrent-manuscript.zip}
\begin{itemize}
    \item \emph{fda-recurrent.tex} : Manuscript TeX File
    \item \emph{si-fda-refs.bib} : Manuscript Bib File
    \item \emph{./figures}: All necessary figures
\end{itemize}
{\bf Supplementary materials zip file:} \emph{fda-recurrent-manuscript.zip}
\begin{itemize}
    \item \emph{fda-recurrent-supplementary.tex} : Supplementary Materials TeX File
    \item \emph{si-fda-refs.bib} : Manuscript Bib File
    \item \emph{./figures}: All necessary figures
\end{itemize}
